Response to reviewers

### 2024-11-29 Manuscript/main_ecography_R1.tex
dent in reviewer 2 comments

For the decreasing size, increasing density and shifting space stressors, we estimated the parameters $\rho$, $D$ and $\rho'$ recursively with the \texttt{dispRity} package to obtain the required amount of data to be removed (\texttt{dispRity::reduce.space}, \citealt{guillerme2018disprity,guillerme2020shifting}).
Note that the algorithm used here to simulate the stressors depends, to some extent, on the distribution of the data for each trait space.
The algorithms used can lead to similar stressor effects depending on the simulated data distribution.
For example, ``increasing density'' and ``decreasing size'' stressors will lead to just what their names suggest if the observations are uniformly distributed (just average increase in density for ``increasing density'' and just overall decrease in size for the ``decreasing size'' stressors) but will have more or less similar effects (albeit not identical) in the case of a normal distribution (average increase in density and overall decrease in size for both ``increasing density'' and ``decreasing size'' stressors.)
These steps resulted in 3420 simulated trait spaces (171 simulated spaces $\times$ 5 stressors $\times$ 4 intensities of data removal).
We used 171 replicates because that was empirically the smallest number of replicates required to reach a variance between replicates lower than 1\% across all metrics (i.e. any additional replicates beyond 171 added less that 1\% extra variance).
See Table \ref{Tab:mechanisms} for a biological description of these stressors and Figure \ref{Fig:simulations} for a visual description of them.

>>>>

For the decreasing size, increasing density and shifting space stressors, we estimated the parameters $\rho$, $D$ and $\rho'$ recursively with the \texttt{dispRity} package to obtain the required amount of data to be removed (\texttt{dispRity::reduce.space}, \citealt{guillerme2018disprity,guillerme2020shifting}).
Note that the algorithm used here to simulate the stressors depends, to some extent, on the distribution of the data for each trait space.
The algorithms used can lead to similar stressor effects depending on the simulated data distribution.
For example, ``increasing density'' and ``decreasing size'' stressors will lead to just what their names suggest if the observations are uniformly distributed (just average increase in density for ``increasing density'' and just overall decrease in size for the ``decreasing size'' stressors) but will have more or less similar effects (albeit not identical) in the case of a normal distribution (average increase in density and overall decrease in size for both ``increasing density'' and ``decreasing size'' stressors).
These steps resulted in 3420 simulated trait spaces (171 simulated spaces $\times$ 5 stressors $\times$ 4 intensities of data removal).
We used 171 replicates because that was empirically the smallest number of replicates required to reach a variance between replicates lower than 1\% across all metrics (i.e. any additional replicates beyond 171 added less that 1\% extra variance).
See Table \ref{Tab:mechanisms} for a biological description of these stressors and Figure \ref{Fig:simulations} for a visual description of them.
